### 2020-03-31 draft_ABP.tex
Updates from Overleaf

@@

\newpage
\section{Stringy canonical forms and $u$-equations for generalized permutahedra}
In this section we shall argue that  a large subset of generalised permutahedra which are realised as degenerations of permutahderon ${\mathscr P_n}$ are binary geometries. Before we proceed we shall review some details about the generalised permutahedra which we shall use throughout the paper.
\subsection{Generalized permutohedra} {\bf the definition, facets and combinatorial factorizations, do $P_n$ example in full details.}
******************************************************************************************
\section*{Permutahedron}
 For $x_1,x_2, \cdots, x_{n+1} \in \mathbb{R} $ , the permutahedron ${\mathscr P_n}(x_1,\cdots,x_{n+1})$ is a convex polytope in $\mathbb{R}^{n+1}$ defined as the convex hull of all vectors obtained from $(x_1,x_2, \cdots, x_{n+1})$ by permutations of the coordinates:
 \bea
{\mathscr P_n}(x_1,x_2, \cdots, x_{n+1}) = {\rm ConvexHull} \{ (x_{w(1)},x_{w(2)}, \cdots, x_{w(n+1)})~ |~ w \in S_{n+1} \}, \nonumber
 \eea
 where $S_{n+1}$ is the symmetric group.

 The permutahedron has $(n+1)!$ vertices and is of dimension at most $n$ since it lies in the hyperplane 
 \bea
 H_c= \{(t_1,t_2, \cdots, t_{n+1}) | t_1 + t_2 + \cdots + t_{n+1}= c \} \subset \mathbb{R}^{n+1}, \nonumber
 \eea
where $c= x_1+x_2+ \cdots +x_{n+1}$.

@@

\subsection*{Generalized permutahedra}

@@

 Unlike the permutahedron not all generalised permutahedra can be represented as a Minkowski sum of co-ordinate simplices. We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation which are called Nestohedra which we denote by ${\mathscr N}$. Throughout the paper we shall mean Nestohedra whenever we refer to generalized permutahedra unless stated otherwise.
 \begin{itemize}
 \item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
  \bea
{\mathscr N_n}^y(\{y_I \})= \sum y_I . \Delta_I  \nonumber
 \eea
 for some collection of subsets $I \in [0,n]$
 \end{itemize}
  \begin{itemize}
 \item{\bf Parameter Independence:} The combinatorial structure of the generalised permutahedron ${\mathscr N_n({y_I})}$ is independent of the parameters $y_I$ and depends only on the collection of subsets $I \in [0,n]$ called the  building set $B$.  \end{itemize}
A collection of non-empty subsets of $[0,n]$ is called a building set $B$ if it satisfies the following:
\begin{compactenum}[\quad (1)]
    \item If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$.
    \item $B$ contains all singletons $\{ i\}$ for $i \in S$.
\end{compactenum}
To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
\subsection*{Nested Complex}
A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
\begin{compactenum}[\quad (1)]
    \item For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
    \item $N$ contains all maximal elements of $B$.
\end{compactenum}
The {\it nested complex} $\mathcal{N}(B)$ is defined as the poset of the set of all nested sets in $B$ ordered by inclusion.

@@

(Chi: I have checked several examples of graph associahedra, there is a conjecture for $u$ variables for this kind of generalized permutohedra: \\
For a element $I$ in the building set $\mathcal{B}$, we define $I_{\text{max}}=\Bigl(\bigcup_{j\sim I} \{j\} \Bigr)\cup I$
where $j\sim I$ means the singleton $j$ is attached to $I$ in the corresponding graph, then 
\begin{equation}
   u_{I} = \prod_{ I \subset J \subset I_{\text{max}}}x_J^{(-1)^{|I|-|J|}}.
\end{equation}
This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.

Based on the above conjecture,  there is a statement for the binary geometries corresponding to the facet $u_{I}\to 0$, 
that is the $u$-system for the facet $u_{I}\to 0$ is corresponding to the generlaized permutohedra $\mathcal{P}_{I}\otimes \mathcal{P}_{\bar{I}}$ with building sets  
\[
\mathcal{B}_{I} = \{J\vert J\subset I, J\in \mathcal{B}\}
\]
and 
\[
\mathcal{B}_{\bar{I}} = \{J-I\vert  J\in \mathcal{B}-\mathcal{B}_{I} \}
\]
where $J-I$ means the complement of $J$ with respect to $I$. This statement directly follow from the fact that $u_{I}\to 0$ is equivalent to take $x_{i}\to t x_{i} $ for $i\in I$ then take $t \to 0$
)

@@

Thus, each $u_I$ is compatible with itself and incompatible with $u^{'}_I$.

>>>>

\usepackage{enumitem}

@@

\newpage
\section{Stringy canonical forms and $u$-equations for generalized permutahedra}
In this section we shall argue that  a large subset of generalised permutahedra which are realised as degenerations of permutahderon ${\mathscr P_n}$ are binary geometries. Before we proceed we shall review some details about the generalised permutahedra which we shall use throughout the paper.
\subsection{Generalized permutohedra} {\bf the definition, facets and combinatorial factorizations, do $P_n$ example in full details.}
******************************************************************************************
\subsubsection*{Permutahedron}
 For $x_1,x_2, \cdots, x_{n+1} \in \mathbb{R} $ , the permutahedron ${\mathscr P_n}(x_1,\cdots,x_{n+1})$ is a convex polytope in $\mathbb{R}^{n+1}$ defined as the convex hull of all vectors obtained from $(x_1,x_2, \cdots, x_{n+1})$ by permutations of the coordinates:
 \bea
{\mathscr P_n}(x_1,x_2, \cdots, x_{n+1}) = {\rm ConvexHull} \{ (x_{w(1)},x_{w(2)}, \cdots, x_{w(n+1)})~ |~ w \in S_{n+1} \}, \nonumber
 \eea
 where $S_{n+1}$ is the symmetric group.

 The permutahedron has $(n+1)!$ vertices and is of dimension at most $n$ since it lies in the hyperplane 
 \bea
 H_c= \{(t_1,t_2, \cdots, t_{n+1}) ~|~ t_1 + t_2 + \cdots + t_{n+1}= c \} \subset \mathbb{R}^{n+1}, \nonumber
 \eea
where $c= x_1+x_2+ \cdots +x_{n+1}$.

@@

\subsubsection*{Generalized permutahedra}

@@

 Unlike the permutahedron not all generalised permutahedra can be represented as a Minkowski sum of co-ordinate simplices. We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation which are called Nestohedra which we denote by ${\mathscr N}$. Throughout the paper we shall mean Nestohedra whenever we refer to generalized permutahedra unless stated otherwise.
 \begin{itemize}
 \item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
  \bea
{\mathscr N_n}^y(\{y_I \})= \sum y_I . \Delta_I  \nonumber
 \eea
 for some collection of subsets $I \in [0,n]$
 \end{itemize}
  \begin{itemize}
 \item{\bf Parameter Independence:} The combinatorial structure of the generalised permutahedron ${\mathscr N_n({y_I})}$ is independent of the parameters $y_I$ and depends only on the collection of subsets $I \in [0,n]$ called the  building set $B$.  \end{itemize}
A collection of non-empty subsets of $[0,n]$ is called a building set $B$ if it satisfies the following:
\begin{compactenum}[\quad (1)]
    \item If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$.
    \item $B$ contains all singletons $\{ i\}$ for $i \in S$.
\end{compactenum}
To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.

\subsubsection*{Nested Complex}
A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
\begin{compactenum}[\quad (1)]
    \item For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
    \item $N$ contains all maximal elements of $B$.
\end{compactenum}
The {\it nested complex} $\mathcal{N}(B)$ is defined as the poset of the set of all nested sets in $B$ ordered by inclusion.

@@

(Chi: I have checked several examples of graph associahedra, there is a conjecture for $u$ variables for this kind of generalized permutohedra: \\
For a element $I$ in the building set $\mathcal{B}$, we define $I_{\text{max}}=\Bigl(\bigcup_{j\sim I} \{j\} \Bigr)\cup I$
where $j\sim I$ means the singleton $j$ is attached to $I$ in the corresponding graph, then 
\begin{equation}
   u_{I} = \prod_{ I \subset J \subset I_{\text{max}}}x_J^{(-1)^{|I|-|J|}}. \label{uvarforgraph}
\end{equation}

\subsubsection{The binary aspects of $u$-variables for graph associahedra}

Here we want to show that the $u_{I}$'s defined in \eqref{uvarforgraph} have the desired binary property, that is, $u_{I}$ and $u_{J}$ are compatible if and only if $I$ and $J$ are one of the following three cases:
\begin{enumerate}
   \item $I\subset J$\:,
   \item $J\subset I$ \:,
   \item $I\cap J=\emptyset$ and $I\cup J \notin \mathcal{B}$ \:.
\end{enumerate}
In other words, this means that $u_{I}$ and $u_{J}$ are incompatible if $I$ and $J$ are one of the following two cases:
\begin{enumerate}[resume]
   \item $I\cap J=\emptyset$ and $I\cup J \in \mathcal{B}$ \:, 
   \item $I\cap J \neq \emptyset,I, J $ \:.
\end{enumerate}

A crucial observation here is that $u_{J}\to 0$ is equivalent to $x_{J}\to 0 $ according to \eqref{uvarforgraph} since all $x_{i}$ are non-negative. We can approach this limit by replacing $x_{j}$ with $ \epsilon x_{j}$ for all $j\in J$ then taking $\epsilon \to 0$. Then the remaining task is just to consider the behaviour of the other $u_{I}$'s under this limit. In the following arrangement, it is convenient to introduce 
\begin{equation}
  p(J_{1},J_{2},\cdots,J_{n}):= \sum_{j\in J } x_{j} \:.
\end{equation}
where $J= \bigcup_{a=1}^{n} J_{a}$

For case (1). First note that if $j\in J$ is not attached to $I$, then $x_{j}$ is independent of $u_{I}$ according to \eqref{uvarforgraph}. Thus, we can decompose $J$ into three parts, 
\begin{equation}
   J= I\cup J_{c}\cup \bar{J}_{c}
\end{equation}
where $J_{c}$ is the set of all singletons in $J$ connected with $I$, $\bar{J}_{c}$ is the set of remaining singletons. Furthermore, We denote $K=I_{\text{max}}-I-J_{c} $ as the set of all singletons which don't belong to $J$ but is connected with $I$. Then we have
\begin{align}
   \lim_{\epsilon \to 0}\log u_{I}&=\lim_{\epsilon \to 0}\sum_{\psi\subset J_{c},\kappa\subset K} (-1)^{\lvert \psi\rvert  +\lvert\kappa\rvert} \log p(I_{\epsilon},\psi_{\epsilon},\kappa) \nonumber \\ 
   &= (-1)^{\lvert \psi\rvert }\sum_{\psi\subset J_{c}}\log p(I,\psi) + \biggl(\log\epsilon +\sum_{\kappa\neq \emptyset}(-1)^{\lvert\kappa\rvert}\log p(\kappa)\biggr)\sum_{\psi\subset J_{c}}(-1)^{\lvert \psi\rvert } \binom{\lvert\psi\rvert }{\lvert J_{c}\rvert } \nonumber \\
   &=  (-1)^{\lvert \psi\rvert }\sum_{\psi\subset J_{c}}\log p(I,\psi) 
     \:,
\end{align}
where $I_{\epsilon}$ and $\psi_{\epsilon}$ indicate that their elements are multiplied with $\epsilon$.

Case (2) and (3) are trivial, we leave them to the reader.

Now let us consider case (4). For this case, we can decompose J into two parts,
\begin{equation}
   J=J_{c}\cup \bar{J}_{c}
\end{equation}
where again $J_{c}$ is the set of all singletons in $J$ connected with $I$, $\bar{J}_{c}$ is the set of remaining singletons. As the above, we denote $K=I_{\text{max}}-I-J_{c} $ as the set of all singletons which don't belong to $J$ but is connected with $I$. Then
\begin{align}
   \lim_{\epsilon \to 0}\log u_{I}&=\lim_{\epsilon \to 0}\sum_{\psi\subset J_{c},\kappa\subset K} (-1)^{\lvert \psi\rvert  +\lvert\kappa\rvert} \log p(I,\psi_{\epsilon},\kappa) \nonumber \\ 
   &= \sum_{\kappa\subset K}(-1)^{\lvert\kappa\rvert}\log p(I,\kappa)\Biggl(\sum_{\psi\subset J_{c}}(-1)^{\lvert \psi\rvert } \binom{\lvert\psi\rvert }{\lvert J_{c}\rvert } \Biggr)\nonumber \\
   &=  0
     \:.
\end{align}
The argument for case (5) is similar with case (4), we omit here.

\paragraph{Quickly review of the facet structure of graph associahedra} Given a graph $\Gamma$ and its subgraph $\Gamma_{J}$, construct a new graph $\Gamma_{J}^{\ast}$ called the reconnected complement: If $V$ and $J$ are the sets of nodes of $\Gamma$ and $\Gamma_{J}$ respectively, then $V-J$ is the set of nodes of $\Gamma_{J}^{\ast}$. There is an edge between nodes $a$ and $b$ in $\Gamma_{J}^{\ast}$ if either $\{a, b\}$ or $\{a, b\}\cup J$ is connected in $\Gamma$. If we denote the corresponding graph associahedron for $\Gamma$ by $\mathcal{P}\Gamma$, then each subgraph $\Gamma_{J}$ corresponds a facet of $\mathcal{P}\Gamma$. In particular, this facet is combinatorially equivalent to $\mathcal{P}\Gamma_{J}\times \mathcal{P}\Gamma_{J}^{\ast}$\cite{}.

It can easily check that, under the limit of $u_{J}\to 0$, $u_{I}$ in case (1) give the $u$-variables for $\mathcal{P}\Gamma_{J}$, while  $u_{I}$ in case (2) and (3) give the $u$-variables for $\mathcal{P}\Gamma_{J}^{\ast}$

{\bf A conjecture for $u$-variables of generalized permutahdera (nextohedra)}

For each element $ I\in \mathcal B$, we define $I^{(0)}=\{I\}$ and  $I^{(1)}$ as the set of all $J\supsetneq I $ such that  $I$ is the ``maximal subset'' of $J$ in $\mathcal{B}$ (that is, there is no $K\in \mathcal{B}$ such that $I\subsetneq K\subsetneq J $). Then, we recursively define 
\begin{equation}
   I^{(i+1)} = \{I^{(i)}_{a}\cup I^{(i)}_{b}\vert I_{a,b}^{(i)}\in I^{(i)},\text{$I_{a}^{(i)}$ and $I_{b}^{(i)}$ are ``maximal subsets'' of $I^{(i)}_{a}\cup I^{(i)}_{b}$ }\}
\end{equation} 
and stop when $\lvert I^{(s)}\rvert =1$. With the defination of $I^{(i)}$, the coresponding $u$-variable is
\begin{equation}
   u_{I} =\prod_{i}(-1)^{i} \prod_{I_{a}^{(i)}\in I^{(i)}} p(I_{a}^{(i)})
\end{equation}

% This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.

% Based on the above conjecture,  there is a statement for the binary geometries corresponding to the facet $u_{I}\to 0$, 
% that is the $u$-system for the facet $u_{I}\to 0$ is corresponding to the generlaized permutohedra $\mathcal{P}_{I}\otimes \mathcal{P}_{\bar{I}}$ with building sets  
% \[
% \mathcal{B}_{I} = \{J\vert J\subset I, J\in \mathcal{B}\}
% \]
% and 
% \[
% \mathcal{B}_{\bar{I}} = \{J-I\vert  J\in \mathcal{B}-\mathcal{B}_{I} \}
% \]
% where $J-I$ means the complement of $J$ with respect to $I$. This statement directly follow from the fact that $u_{I}\to 0$ is equivalent to take $x_{i}\to t x_{i} $ for $i\in I$ then take $t \to 0$
% )

@@

% Thus, each $u_I$ is compatible with itself and incompatible with $u^{'}_I$.
